```{r}
## Dredge tests 

citation("vegan") #this is to cite any package

```

```{r}
library(MuMIn)
#checking which variable has highest effect 
#checking which is best model
## preparing the linear model with all parameters and some interactions
#Morans Local, FinalFileMoranLocal
#Morans Global, global_param_updated
#Mantel Local, MantelParamLocal
#Mantel Global, global_param
MantelGlobalFullModel = lm(Mantelglobal ~ Yard.Difference + 
                    Neighbor.Distance +
                    Comparison.Type +
                    Comparison.Type:Neighbor.Distance +
                    Yard.Difference:Neighbor.Distance +
                    Yard.Difference:Comparison.Type, 
                  data = global_param) 


## Model selection procedure: 
options(na.action = "na.fail")  

dd = dredge(MantelGlobalFullModel)
# View the top models
head(dd)

#this is for variable estimates 
summary(MantelGlobalFullModel)

## Best model summary: this takes out the worst variables to give you best model 
summary(get.models(dd, 1)[[1]])
```

```{r}

```
MantelGlobalFullModel = lm(Mantelglobal ~ Yard.Difference + 
                    Neighbor.Distance +
                    Comparison.Type +
                    Comparison.Type:Neighbor.Distance +
                    Yard.Difference:Neighbor.Distance +
                    Yard.Difference:Comparison.Type, 
                  data = global_param) 


## Model selection procedure: 
options(na.action = "na.fail")  

dd = dredge(MantelGlobalFullModel)
# View the top models
head(dd)

#this is for variable estimates 
summary(MantelGlobalFullModel)

